Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-07 paper.tex
Add more modifications from jpl comments.

\textbf{In this paper, we present a planning algorithm that considers
  exact models of a humanoid robot and its environment. It is used to
  solve navigation and manipulation problems. Our planner is a
  two-step algorithm: a first collision-free path is computed in the
  quasi-static configuration space \footnote{A quasi-static
    configuration is a configuration where the robot is balanced on
    its feet with zero speed.}, then this first path is approximated
  by a sequence of dynamic walking trajectories. The proof of
  correctness of the algorithm is based on the concept of small-space
  controllability. Such property allows to approximate any \textit{non
    necessarily admissible} path, by a sequence of admissible ones. In
  our context we prove that dynamic walking makes humanoid robots
  small-space controllable. Our planner is designed for perfectly
  modeled indoor environments, where the floor is horizontal and
  flat. Also, because we do not explicitly compute footprint positions
  at the planning stage, the presented planner is unable to plan
  motions in which the robot steps over obstacles. These limitations
  are discussed in the paper.}

@@

\textbf{The constrained motion planner and the small-space
  controllability property can luckily still be used with different
  environment representations that might more suited with perception
  systems and their inherent measurement errors, using for instance
  point clouds. In the future, we would like to achieve dynamic walk
  planning using a Kinect sensor that would be mounted on the humanoid
  robot. This would relax the a priori environment knowledge
  constraint and bring us one step closer to reactive planning in
  unknown environments.}

>>>>

\textbf{In this paper, we present a planning algorithm that considers
  exact models of a humanoid robot and its environment. It is used to
  solve navigation and manipulation problems. Our planner is a
  two-step algorithm: a first collision-free path is computed in the
  space of quasi-statically balanced configurations, then this first
  path is approximated by a sequence of dynamic walking trajectories,
  i.e. trajectories satisfying the Newton-Euler equations. The proof
  of correctness of the algorithm is based on the concept of
  small-space controllability. This property allows, under some
  assumptions, to approximate any \textit{non necessarily admissible}
  path, by a sequence of admissible trajectories. In our context we
  prove that dynamic walking makes humanoid robots small-space
  controllable. Our planner is designed for perfectly modeled indoor
  environments, where the floor is horizontal and flat. Also, because
  we do not explicitly compute footprint positions at the planning
  stage, the presented planner is unable to plan motions in which the
  robot steps over obstacles. These limitations are discussed in the
  paper.}

@@

\textbf{Our constrained motion planner and the small-space
  controllability property can luckily still be used with different
  environment representations that might be more suited with
  perception systems. Extensions in that directions
  \cite{Nakhei4755945, Dang6100889} are currently under development to
  relax the a priori environment knowledge constraint and achieve
  reactive planning in unknown environments.}
